---
title: "K9_Analysis"
author: "Grace Layman"
date: "2025-04-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis on K9 Stake 2022

## Total amount of species observed

```{r}
#Loading necessary libraries 
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(tidyr)
```

```{r}
# Looking at Species Observations Across the Year 
k9_total <- read.csv("C:/git/MasonFarmARUs/data/2022_k9_filtered.csv")
speciesList <- read.csv("C:/git/MasonFarmARUs/data/species_list_csvCopy.csv")
species <- speciesList$Common.Name
julian_days <- 151:201
complete_days <- crossing(Common.name = species, julian_day = julian_days)

num_species <- k9_total |>
  count(Common.name)|>
  arrange(desc(n))|>
  glimpse()


# Want to make a dataframe that has all the combinations of julian days and species
species_by_day <- k9_total |>
  group_by(julian_day,)|>
  count(Common.name)|>
  arrange(desc(n)) |>
  glimpse()

species_day <- complete_days|>
  left_join(species_by_day, by = c("Common.name", "julian_day"))|>
  mutate(n = replace_na(n,0))

#write.csv(species_day,"data/species_by_day.csv")
```

I will be looking at seasonal and temporal variation in species abundance with the six species that were observed the most by Birdnet over the summer. This data is stored in the num_species data frame above. In order, these species are: Acadian Flycatcher, Summer Tanager, Yellow-throated Vireo, Eastern Wood-Pewee, Tufted Titmouse, and Scarlet Tanager.

## Basic Stats on Observations

```{r}
k9_stats<- k9_total%>%
  group_by(Common.name) %>% 
  summarize(medianConf = median(Confidence),
            maxConf = max(Confidence),
            minConf = min(Confidence)) %>% 
  arrange(desc(maxConf)) %>% data.frame()|>
  glimpse()
```

## Trends Across the Six Species

```{r plotting-jdVspecies, fig.path='figures/k9/'}

png("C:/git/MasonFarmARUs/figures/jdVdect.png", width = 800, height = 600)

#Mapping Julian Day Versus the Number of Observations for the top Seven Species
filtered_AF <- species_day[species_day$Common.name == "Acadian Flycatcher", ]
plot(filtered_AF$julian_day,
     filtered_AF$n, 
     xlab = "Julian Day",
     ylab = "Number of Vocalizations", 
     ylim = c(0, 1000), xlim = c(151,201),
     type = 'l',
     col = 'lightgoldenrod', 
     lwd = 2)
filtered_ST <- species_day[species_day$Common.name == "Summer Tanager", ]
points(filtered_ST$julian_day, 
       filtered_ST$n,
       type = 'l',
       col = "lightblue",
       lwd = 2)
filtered_YV <- species_day[species_day$Common.name == "Yellow-throated Vireo", ]
points(filtered_YV$julian_day, 
       filtered_YV$n,
       type = 'l',
       col = "lightgreen",
       lwd = 2)
filtered_EP <- species_day[species_day$Common.name == "Eastern Wood-Pewee", ]
points(filtered_EP$julian_day, 
       filtered_EP$n,
       type = 'l',
       col = "lightcoral",
       lwd = 2)
filtered_TT <- species_day[species_day$Common.name == "Tufted Titmouse", ]
points(filtered_TT$julian_day, 
       filtered_TT$n,
       type = 'l',
       col = "plum3",
       lwd = 2)
filtered_SCT <- species_day[species_day$Common.name == "Scarlet Tanager", ]
points(filtered_SCT$julian_day, 
       filtered_SCT$n,
       type = 'l',
       col = "royalblue",
       lwd = 2)
legend("topright", legend = c("Acadian Flycatcher",
                              "Summer Tanager",
                              "Yellow-throated Vireo",
                              "Eastern Wood-Pewee",
                              "Tufted Titmouse",
                              "Scarlet Tanager"),
       col = c("lightgoldenrod", "lightblue", "lightgreen", "lightcoral", "plum3", "royalblue"),
       lwd = 2)
dev.off()
```

## Analyzing Acadian Flycatcher Patterns 

Acadian Flycatcher was the species detected at Mason Farm the most. There were 7900 detections of Acadian Flycatchers from julian day 151 to 201.

```{r}
# Creating 10 minute bins for the observations 
AF_bins <- k9_total |>
  filter(Common.name == "Acadian Flycatcher") |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(start/900))

```

```{r}
# Plotting number of detections per minute bin 
AF_minVdect <- AF_bins |>
  group_by(min_bin)|>
  summarize(num_detections = n())

png("C:/git/MasonFarmARUs/figures/AF_bar_all.png", width = 800, height = 600)
ggplot(AF_minVdect, aes(x = min_bin , y = num_detections, fill)) +
  geom_bar(stat = "identity") +
  labs(x = "Ten Minute Interval", y = "Number of Detections", title = "Number of Acadian Flycatcher Detections Per 10 Minute Intervals Across Summer 2022") 
  theme_minimal()
dev.off()
```

```{r}
png("C:/git/MasonFarmARUs/figures/AF_time_periods.png", width = 800, height = 600)

# The number of vocalizations per 15 minute time periods throughout the summer 
library(ggplot2)
ggplot(AF_dectVday, aes(x= julian_day, y= num_dect))+
  geom_line(color = "lightgoldenrod", size = 1) +  # Line plot for each time period
  labs(
    x = "Julian Day",
    y = "Number of Vocalizations",
    title = "Number of Vocalizations Across 15 Minute Time Periods"
  ) +
  theme_minimal() +  # Clean theme
  facet_wrap(~min_bin, ncol = 3)  # Create facets with 3 columns
dev.off()
```

## Analyzing Summer Tanager Patterns

The second most commonly detected bird was the Summer Tanager. The Summer Tanager was detected 6083 times.

## Analyzing Yellow-throated Vireo Patterns

## Analyzing Eastern Wood-Pewee Patterns

## Analyzing Tufted Titmouse Patterns 

## Analyzing Scarlet Tanager Patterns 
