---
title: "K9_Analysis"
author: "Grace Layman"
date: "2025-04-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis on K9 Stake 2022

## Total amount of species observed

```{r}
#Loading necessary libraries 
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(tibble)
```

```{r}
# Looking at Species Observations Across the Year 
k9_total <- read.csv("C:/git/MasonFarmARUs/data/2022_k9_filtered.csv")
speciesList <- read.csv("C:/git/MasonFarmARUs/data/species_list_csvCopy.csv")
species <- speciesList$Common.Name
julian_days <- 151:201
complete_days <- crossing(Common.name = species, julian_day = julian_days)

num_species <- k9_total |>
  count(Common.name)|>
  arrange(desc(n))|>
  glimpse()


# Want to make a dataframe that has all the combinations of julian days and species
species_by_day <- k9_total |>
  group_by(julian_day,)|>
  count(Common.name)|>
  arrange(desc(n)) |>
  glimpse()

species_day <- complete_days|>
  left_join(species_by_day, by = c("Common.name", "julian_day"))|>
  mutate(n = replace_na(n,0))

#write.csv(species_day,"data/species_by_day.csv")
```

I will be looking at seasonal and temporal variation in species abundance with the six species that were observed the most by Birdnet over the summer. This data is stored in the num_species data frame above. In order, these species are: Acadian Flycatcher, Summer Tanager, Yellow-throated Vireo, Eastern Wood-Pewee, Tufted Titmouse, and Scarlet Tanager.

## Basic Stats on Observations

```{r}
k9_stats<- k9_total%>%
  group_by(Common.name) %>% 
  summarize(medianConf = median(Confidence),
            maxConf = max(Confidence),
            minConf = min(Confidence)) %>% 
  arrange(desc(maxConf)) %>% data.frame()|>
  glimpse()
```

## Trends Across the Six Species

```{r plotting-jdVspecies, fig.path='figures/k9/'}

#png("C:/git/MasonFarmARUs/figures/jdVdect.png", width = 800, height = 600)

#Mapping Julian Day Versus the Number of Observations for the top Seven Species
filtered_AF <- species_day[species_day$Common.name == "Acadian Flycatcher", ]
plot(filtered_AF$julian_day,
     filtered_AF$n, 
     xlab = "Julian Day",
     ylab = "Number of Vocalizations", 
     ylim = c(0, 1000), xlim = c(151,201),
     type = 'l',
     col = 'lightgoldenrod', 
     lwd = 2)
filtered_ST <- species_day[species_day$Common.name == "Summer Tanager", ]
points(filtered_ST$julian_day, 
       filtered_ST$n,
       type = 'l',
       col = "lightblue",
       lwd = 2)
filtered_YV <- species_day[species_day$Common.name == "Yellow-throated Vireo", ]
points(filtered_YV$julian_day, 
       filtered_YV$n,
       type = 'l',
       col = "lightgreen",
       lwd = 2)
filtered_EP <- species_day[species_day$Common.name == "Eastern Wood-Pewee", ]
points(filtered_EP$julian_day, 
       filtered_EP$n,
       type = 'l',
       col = "lightcoral",
       lwd = 2)
filtered_TT <- species_day[species_day$Common.name == "Tufted Titmouse", ]
points(filtered_TT$julian_day, 
       filtered_TT$n,
       type = 'l',
       col = "plum3",
       lwd = 2)
filtered_SCT <- species_day[species_day$Common.name == "Scarlet Tanager", ]
points(filtered_SCT$julian_day, 
       filtered_SCT$n,
       type = 'l',
       col = "royalblue",
       lwd = 2)
legend("topright", legend = c("Acadian Flycatcher",
                              "Summer Tanager",
                              "Yellow-throated Vireo",
                              "Eastern Wood-Pewee",
                              "Tufted Titmouse",
                              "Scarlet Tanager"),
       col = c("lightgoldenrod", "lightblue", "lightgreen", "lightcoral", "plum3", "royalblue"),
       lwd = 2)
#dev.off()
```

```{r}
# Full dataframe with minute bins 

day_mins<- k9_total |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))

# Creating a dataframe with every species, min_bin, and date possible 

all_julian <- min(k9_total$julian_day):max(k9_total$julian_day)
species_vec <- speciesList$Common.Name
julian_vec <- as.integer(all_julian)
min_bin_vec <- day_mins$min_bin

all_combos <- expand.grid(
  Bird.Call = species_vec,
  julian_day = julian_vec,
  min_bin = min_bin_vec
)

target_species <- c(
  "Acadian Flycatcher", 
  "Summer Tanager", 
  "Yellow-throated Vireo", 
  "Eastern Wood-Pewee", 
  "Tufted Titmouse", 
  "Scarlet Tanager"
)
```

## Matrix Mapping

```{r}

bird_counts <- day_mins |>
  filter(Common.name %in% target_species)|>
  count(Common.name, julian_day, min_bin)

full_counts <- all_combos |>
  filter(Bird.Call %in% target_species)|>
  left_join(bird_counts, by = c("Bird.Call" = "Common.name", "julian_day", "min_bin")) |>
  mutate(n = replace_na(n, 0))

# Get unique combinations of Bird.Call, julian_day, min_bin, and n
full_counts_clean <- full_counts |>
  distinct(Bird.Call, julian_day, min_bin, n, .keep_all = TRUE)
```

### Acadian Flycatcher Matrix

```{r}
af_matrix <- full_counts_clean |>
  filter(Bird.Call == "Acadian Flycatcher") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

af_matrix_numeric <- af_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(af_matrix_numeric, axes = FALSE, col = rev(heat.colors(256)))

axis(1, at = seq(0, 1, length.out = ncol(af_matrix_numeric)), labels = colnames(af_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(af_matrix_numeric)), labels = rownames(af_matrix_numeric))
# Add title and axis labels
title(main = "Acadian Flycatcher Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Summer Tanager Matrix

```{r}
st_matrix<- full_counts_clean |>
  filter(Bird.Call == "Summer Tanager") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

st_matrix_numeric <- st_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(st_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "lightblue", "navy"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(st_matrix_numeric)), labels = colnames(st_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(st_matrix_numeric)), labels = rownames(st_matrix_numeric))
# Add title and axis labels
title(main = "Summer Tanager Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Yellow-throated Vireo Matrix

```{r}
yv_matrix<- full_counts_clean |>
  filter(Bird.Call == "Yellow-throated Vireo") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

yv_matrix_numeric <- yv_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(yv_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "green", "darkgreen"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(yv_matrix_numeric)), labels = colnames(yv_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(yv_matrix_numeric)), labels = rownames(yv_matrix_numeric))
# Add title and axis labels
title(main = "Yellow-throated Vireo Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Eastern Wood-Pewee Matrix

```{r}
ep_matrix<- full_counts_clean |>
  filter(Bird.Call == "Eastern Wood-Pewee") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

ep_matrix_numeric <- ep_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(ep_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "pink", "hotpink4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(ep_matrix_numeric)), labels = colnames(ep_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(ep_matrix_numeric)), labels = rownames(ep_matrix_numeric))
# Add title and axis labels
title(main = "Eastern Wood-Pewee Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Tufted Titmouse Matrix 

```{r}
tt_matrix<- full_counts_clean |>
  filter(Bird.Call == "Tufted Titmouse") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

tt_matrix_numeric <- tt_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(tt_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "plum", "purple4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(tt_matrix_numeric)), labels = colnames(tt_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(tt_matrix_numeric)), labels = rownames(tt_matrix_numeric))
# Add title and axis labels
title(main = "Tufted Titmouse Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Scarlet Tanager Matrix

```{r}
tt_matrix<- full_counts_clean |>
  filter(Bird.Call == "Tufted Titmouse") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

tt_matrix_numeric <- tt_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(tt_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "plum", "purple4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(tt_matrix_numeric)), labels = colnames(tt_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(tt_matrix_numeric)), labels = rownames(tt_matrix_numeric))
# Add title and axis labels
title(main = "Tufted Titmouse Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Analyzing Acadian Flycatcher Pattern

Acadian Flycatcher was the species detected at Mason Farm the most. There were 7900 detections of Acadian Flycatchers from julian day 151 to 201.

```{r}
# Creating 10 minute bins for the observations 
AF_bins <- k9_total |>
  filter(Common.name == "Acadian Flycatcher") |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))

```

```{r}
# Plotting number of detections per minute bin 
AF_minVdect <- AF_bins |>
  group_by(min_bin)|>
  summarize(num_detections = n())

#png("C:/git/MasonFarmARUs/figures/AF_bar_all.png", width = 800, height = 600)
ggplot(AF_minVdect, aes(x = min_bin , y = num_detections, fill)) +
  geom_bar(stat = "identity") +
  labs(x = "Ten Minute Interval", y = "Number of Detections", title = "Number of Acadian Flycatcher Detections Per 10 Minute Intervals Across Summer 2022") 
  theme_minimal()
#dev.off()
```

```{r}
#Creating a dataframe with the counts of ST for each day
AF_counts <- AF_bins |>
  count(Common.name, julian_day, min_bin)|>
  filter(Common.name == "Acadian Flycatcher")

AF_dectVday <- all_combos |>
  filter(Bird.Call == "Acadian Flycatcher") |>
  left_join(AF_counts, by = c("Bird.Call"= "Common.name", "julian_day", "min_bin")) %>%
  mutate(n = replace_na(n, 0))
```

```{r}
#png("C:/git/MasonFarmARUs/figures/AF_time_periods.png", width = 800, height = 600)

# The number of vocalizations per 15 minute time periods throughout the summer 
library(ggplot2)
ggplot(AF_dectVday, aes(x= julian_day, y= n))+
  geom_line(color = "lightgoldenrod", linewidth = 1) +  # Line plot for each time period
  labs(
    x = "Julian Day",
    y = "Number of Vocalizations",
    title = "Acadian Flycatcher Vocalizations Across 15 Minute Time Periods"
  ) +
  theme_minimal() +  # Clean theme
  facet_wrap(~min_bin, ncol = 3)  # Create facets with 3 columns
#dev.off()
```

## Analyzing Summer Tanager Patterns

The second most commonly detected bird was the Summer Tanager. The Summer Tanager was detected 6083 times.

```{r}
# Creating 10 minute bins for the observations 
ST_bins <- k9_total |>
  filter(Common.name == "Summer Tanager") |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))
```

```{r}
# Plotting number of detections per minute bin 
ST_minVdect <- ST_bins |>
  group_by(min_bin)|>
  summarize(num_detections = n())

#png("C:/git/MasonFarmARUs/figures/ST_bar_all.png", width = 800, height = 600)
ggplot(ST_minVdect, aes(x = min_bin , y = num_detections, fill)) +
  geom_bar(stat = "identity") +
  labs(x = "Ten Minute Interval", y = "Number of Detections", title = "Number of Summer Tanagers Detections Per 10 Minute Intervals Across Summer 2022") 
  theme_minimal()
#dev.off()
```

```{r}
#Creating a dataframe with the counts of ST for each day
ST_counts <- ST_bins |>
  count(Common.name, julian_day, min_bin)|>
  filter(Common.name == "Summer Tanager")

ST_dectVday <- all_combos |>
  filter(Bird.Call == "Summer Tanager") |>
  left_join(ST_counts, by = c("Bird.Call"= "Common.name", "julian_day", "min_bin")) %>%
  mutate(n = replace_na(n, 0))
```

```{r}
#png("C:/git/MasonFarmARUs/figures/ST_time_periods.png", width = 800, height = 600)

# The number of vocalizations per 15 minute time periods throughout the summer 
library(ggplot2)
ggplot(ST_dectVday, aes(x= julian_day, y= n))+
  geom_line(color = "lightblue", linewidth = 1) +  # Line plot for each time period
  labs(
    x = "Julian Day",
    y = "Number of Vocalizations",
    title = "Number of Summer Tanagers Vocalizations Across 15 Minute Time Periods"
  ) +
  theme_minimal() +  # Clean theme
  facet_wrap(~min_bin, ncol = 3)  # Create facets with 3 columns
#dev.off()
```

## Analyzing Yellow-throated Vireo Patterns

```{r}
# Creating 10 minute bins for the observations 
YV_bins <- k9_total |>
  filter(Common.name == "Yellow-throated Vireo") |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))
```

```{r}
# Plotting number of detections per minute bin 
YV_minVdect <- YV_bins |>
  group_by(min_bin)|>
  summarize(num_detections = n())

#png("C:/git/MasonFarmARUs/figures/YV_bar_all.png", width = 800, height = 600)
ggplot(YV_minVdect, aes(x = min_bin , y = num_detections, fill)) +
  geom_bar(stat = "identity") +
  labs(x = "Ten Minute Interval", y = "Number of Detections", title = "Number of Yellow-throated Vireo Detections Per 10 Minute Intervals Across Summer 2022") 
  theme_minimal()
#dev.off()
```

```{r}
#Creating a dataframe with the counts of YV for each day
YV_counts <- YV_bins |>
  count(Common.name, julian_day, min_bin)|>
  filter(Common.name == "Yellow-throated Vireo")

YV_dectVday <- all_combos |>
  filter(Bird.Call == "Yellow-throated Vireo") |>
  left_join(YV_counts, by = c("Bird.Call"= "Common.name", "julian_day", "min_bin")) %>%
  mutate(n = replace_na(n, 0))
```

```{r}
#png("C:/git/MasonFarmARUs/figures/YV_time_periods.png", width = 800, height = 600)

# The number of vocalizations per 15 minute time periods throughout the summer 
library(ggplot2)
ggplot(YV_dectVday, aes(x= julian_day, y= n))+
  geom_line(color = "lightgreen", linewidth = 1) +  # Line plot for each time period
  labs(
    x = "Julian Day",
    y = "Number of Vocalizations",
    title = "Number of Yellow-throated Vireos Vocalizations Across 15 Minute Time Periods"
  ) +
  theme_minimal() +  # Clean theme
  facet_wrap(~min_bin, ncol = 3)  # Create facets with 3 columns
#dev.off()
```

## Analyzing Eastern Wood-Pewee Patterns

```{r}
# Creating 10 minute bins for the observations 
EP_bins <- k9_total |>
  filter(Common.name == "Eastern Wood-Pewee") |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))
```

```{r}
# Plotting number of detections per minute bin 
EP_minVdect <- EP_bins |>
  group_by(min_bin)|>
  summarize(num_detections = n())

#png("C:/git/MasonFarmARUs/figures/EP_bar_all.png", width = 800, height = 600)
ggplot(EP_minVdect, aes(x = min_bin , y = num_detections, fill)) +
  geom_bar(stat = "identity") +
  labs(x = "Ten Minute Interval", y = "Number of Detections", title = "Number of Eastern Wood-Pewee Detections Per 10 Minute Intervals Across Summer 2022") 
  theme_minimal()
#dev.off()
```

```{r}
#Creating a dataframe with the counts of YV for each day
EP_counts <- EP_bins |>
  count(Common.name, julian_day, min_bin)|>
  filter(Common.name == "Eastern Wood-Pewee")

EP_dectVday <- all_combos |>
  filter(Bird.Call == "Eastern Wood-Pewee") |>
  left_join(EP_counts, by = c("Bird.Call"= "Common.name", "julian_day", "min_bin")) %>%
  mutate(n = replace_na(n, 0))
```

```{r}
#png("C:/git/MasonFarmARUs/figures/EP_time_periods.png", width = 800, height = 600)

# The number of vocalizations per 15 minute time periods throughout the summer 
library(ggplot2)
ggplot(EP_dectVday, aes(x= julian_day, y= n))+
  geom_line(color = "lightcoral", linewidth = 1) +  # Line plot for each time period
  labs(
    x = "Julian Day",
    y = "Number of Vocalizations",
    title = "Number of Eastern Wood-Pewee Vocalizations Across 15 Minute Time Periods"
  ) +
  theme_minimal() +  # Clean theme
  facet_wrap(~min_bin, ncol = 3)  # Create facets with 3 columns
#dev.off()
```

## Analyzing Tufted Titmouse Patterns

```{r}
# Creating 10 minute bins for the observations 
TT_bins <- k9_total |>
  filter(Common.name == "Tufted Titmouse") |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))
```

```{r}
# Plotting number of detections per minute bin 
TT_minVdect <- TT_bins |>
  group_by(min_bin)|>
  summarize(num_detections = n())

#png("C:/git/MasonFarmARUs/figures/TT_bar_all.png", width = 800, height = 600)
ggplot(TT_minVdect, aes(x = min_bin , y = num_detections, fill)) +
  geom_bar(stat = "identity") +
  labs(x = "Ten Minute Interval", y = "Number of Detections", title = "Number of Tufted Titmouse Detections Per 10 Minute Intervals Across Summer 2022") 
  theme_minimal()
#dev.off()
```

```{r}
#Creating a dataframe with the counts of YV for each day
TT_counts <- TT_bins |>
  count(Common.name, julian_day, min_bin)|>
  filter(Common.name == "Tufted Titmouse")

TT_dectVday <- all_combos |>
  filter(Bird.Call == "Tufted Titmouse") |>
  left_join(TT_counts, by = c("Bird.Call"= "Common.name", "julian_day", "min_bin")) %>%
  mutate(n = replace_na(n, 0))
```

```{r}
#png("C:/git/MasonFarmARUs/figures/TT_time_periods.png", width = 800, height = 600)

# The number of vocalizations per 15 minute time periods throughout the summer 
library(ggplot2)
ggplot(TT_dectVday, aes(x= julian_day, y= n))+
  geom_line(color = "plum3", linewidth = 1) +  # Line plot for each time period
  labs(
    x = "Julian Day",
    y = "Number of Vocalizations",
    title = "Number of Tufted Titmouse Vocalizations Across 15 Minute Time Periods"
  ) +
  theme_minimal() +  # Clean theme
  facet_wrap(~min_bin, ncol = 3)  # Create facets with 3 columns
#dev.off()
```

## Analyzing Scarlet Tanager Patterns

```{r}
# Creating 10 minute bins for the observations 
SCT_bins <- k9_total |>
  filter(Common.name == "Scarlet Tanager") |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))
```

```{r}
# Plotting number of detections per minute bin 
SCT_minVdect <- SCT_bins |>
  group_by(min_bin)|>
  summarize(num_detections = n())

#png("C:/git/MasonFarmARUs/figures/SCT_bar_all.png", width = 800, height = 600)
ggplot(SCT_minVdect, aes(x = min_bin , y = num_detections, fill)) +
  geom_bar(stat = "identity") +
  labs(x = "Ten Minute Interval", y = "Number of Detections", title = "Number of Scarlet Tanager Detections Per 10 Minute Intervals Across Summer 2022") 
  theme_minimal()
#dev.off()
```

```{r}
#Creating a dataframe with the counts of YV for each day
SCT_counts <- SCT_bins |>
  count(Common.name, julian_day, min_bin)|>
  filter(Common.name == "Scarlet Tanager")

SCT_dectVday <- all_combos |>
  filter(Bird.Call == "Scarlet Tanager") |>
  left_join(SCT_counts, by = c("Bird.Call"= "Common.name", "julian_day", "min_bin")) %>%
  mutate(n = replace_na(n, 0))
```

```{r}
#png("C:/git/MasonFarmARUs/figures/SCT_time_periods.png", width = 800, height = 600)

# The number of vocalizations per 15 minute time periods throughout the summer 
library(ggplot2)
ggplot(SCT_dectVday, aes(x= julian_day, y= n))+
  geom_line(color = "royalblue", linewidth = 1) +  # Line plot for each time period
  labs(
    x = "Julian Day",
    y = "Number of Vocalizations",
    title = "Number of Scarlet Tanager Vocalizations Across 15 Minute Time Periods"
  ) +
  theme_minimal() +  # Clean theme
  facet_wrap(~min_bin, ncol = 3)  # Create facets with 3 columns
#dev.off()
```
