---
title: "K9_Analysis"
author: "Grace Layman"
date: "2025-04-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis on K9 Stake 2022

## Total amount of species observed

```{r}
#Loading necessary libraries 
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(tibble)
```

```{r}
# Looking at Species Observations Across the Year 
k9_total <- read.csv("C:/git/MasonFarmARUs/data/2022_k9_filtered.csv")
speciesList <- read.csv("C:/git/MasonFarmARUs/data/species_list_csvCopy.csv")
species <- speciesList$Common.Name
julian_days <- 151:201
complete_days <- crossing(Common.name = species, julian_day = julian_days)

num_species <- k9_total |>
  count(Common.name)|>
  arrange(desc(n))|>
  glimpse()


# Want to make a dataframe that has all the combinations of julian days and species
species_by_day <- k9_total |>
  group_by(julian_day,)|>
  count(Common.name)|>
  arrange(desc(n)) |>
  glimpse()

species_day <- complete_days|>
  left_join(species_by_day, by = c("Common.name", "julian_day"))|>
  mutate(n = replace_na(n,0))

#write.csv(species_day,"data/species_by_day.csv")
```

I will be looking at seasonal and temporal variation in species abundance with the six species that were observed the most by Birdnet over the summer. This data is stored in the num_species data frame above. In order, these species are: Acadian Flycatcher, Summer Tanager, Yellow-throated Vireo, Eastern Wood-Pewee, Tufted Titmouse, and Scarlet Tanager.

## Basic Stats on Observations

```{r}
k9_stats<- k9_total%>%
  group_by(Common.name) %>% 
  summarize(medianConf = median(Confidence),
            maxConf = max(Confidence),
            minConf = min(Confidence)) %>% 
  arrange(desc(maxConf)) %>% data.frame()|>
  glimpse()
```

## Trends Across the Six Species

```{r plotting-jdVspecies, fig.path='figures/k9/'}

#png("C:/git/MasonFarmARUs/figures/jdVdect.png", width = 1200, height =1000)
par(mar = c(5, 5, 4, 2) + 2.3,
     mgp = c(4.1, 1, 0))
# Mapping Julian Day Versus the Number of Observations for the top Seven Species
filtered_AF <- species_day[species_day$Common.name == "Acadian Flycatcher", ]
plot(filtered_AF$julian_day,
     filtered_AF$n, 
     xlab = "Day of Year (DOY)",
     ylab = "Number of Vocalizations", 
     ylim = c(0, 1000), 
     xlim = c(151, 201),
     type = 'l',
     col = 'lightgoldenrod', 
     lwd = 2,
     xaxt = 'n',
     cex.lab = 3.0,
     cex.axis = 2.5)  # This suppresses the default x-axis

# Add custom x-axis
#axis(1, at = seq(151, 201, by = 10), labels = seq(151, 201, by = 10), cex.axis=2.5)
# Or for month-day labels:
axis(1, at = c(152, 167, 182, 197), labels = c("Jun-1", "Jun-16", "Jul-1", "Jul-16"), cex.axis=2.5)

filtered_ST <- species_day[species_day$Common.name == "Summer Tanager", ]
points(filtered_ST$julian_day, 
       filtered_ST$n,
       type = 'l',
       col = "lightblue",
       lwd = 2)

filtered_YV <- species_day[species_day$Common.name == "Yellow-throated Vireo", ]
points(filtered_YV$julian_day, 
       filtered_YV$n,
       type = 'l',
       col = "lightgreen",
       lwd = 2)

filtered_EP <- species_day[species_day$Common.name == "Eastern Wood-Pewee", ]
points(filtered_EP$julian_day, 
       filtered_EP$n,
       type = 'l',
       col = "lightcoral",
       lwd = 2)

filtered_TT <- species_day[species_day$Common.name == "Tufted Titmouse", ]
points(filtered_TT$julian_day, 
       filtered_TT$n,
       type = 'l',
       col = "plum3",
       lwd = 2)

filtered_SCT <- species_day[species_day$Common.name == "Scarlet Tanager", ]
points(filtered_SCT$julian_day, 
       filtered_SCT$n,
       type = 'l',
       col = "royalblue",
       lwd = 2)

legend("topright", 
       legend = c("Acadian Flycatcher",
                  "Summer Tanager",
                  "Yellow-throated Vireo",
                  "Eastern Wood-Pewee",
                  "Tufted Titmouse",
                  "Scarlet Tanager"),
       col = c("lightgoldenrod", "lightblue", "lightgreen", "lightcoral", "plum3", "royalblue"),
       lwd = 2,
       cex = 2.0)
#dev.off()
```

```{r}
# Full dataframe with minute bins 

day_mins<- k9_total |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))

# Creating a dataframe with every species, min_bin, and date possible 

all_julian <- min(k9_total$julian_day):max(k9_total$julian_day)
species_vec <- speciesList$Common.Name
julian_vec <- as.integer(all_julian)
min_bin_vec <- day_mins$min_bin

all_combos <- expand.grid(
  Bird.Call = species_vec,
  julian_day = julian_vec,
  min_bin = min_bin_vec
)

target_species <- c(
  "Acadian Flycatcher", 
  "Summer Tanager", 
  "Yellow-throated Vireo", 
  "Eastern Wood-Pewee", 
  "Tufted Titmouse", 
  "Scarlet Tanager"
)
```

## Matrix Mapping

```{r}

bird_counts <- day_mins |>
  filter(Common.name %in% target_species)|>
  count(Common.name, julian_day, min_bin)

full_counts <- all_combos |>
  filter(Bird.Call %in% target_species)|>
  left_join(bird_counts, by = c("Bird.Call" = "Common.name", "julian_day", "min_bin")) |>
  mutate(n = replace_na(n, 0))

# Get unique combinations of Bird.Call, julian_day, min_bin, and n
full_counts_clean <- full_counts |>
  distinct(Bird.Call, julian_day, min_bin, n, .keep_all = TRUE)
#write.csv(full_counts_clean,"C:/git/MasonFarmARUs/data/full_counts_clean.csv")
```

### Matrix X & Y Labels Creation

```{r}
# Creating X Axis (Time of day) labels
tick_y <- c(1, 2, 4, 6, 8, 10, 12)
tick_at_y <- (tick_y -1)/ (ncol(af_matrix) -1)
tick_labels_y <- c("5:45", "6:00", "6:30", "7:00", "7:30", "8:00", "8:30")

tick_x <- c(3, 18, 33, 48, 51)
tick_at_x <- (tick_x - 1)/ (nrow(af_matrix) - 1)
tick_labels_x <- c( "June 1", "June 16", "July 1", "July 16", "July 19")
```

### Acadian Flycatcher Matrix

```{r}
full_counts_clean <- read.csv("C:/git/MasonFarmARUs/data/full_counts_clean.csv")
full_counts_clean$min_bin <- as.character(full_counts_clean$min_bin)

png("C:/git/MasonFarmARUs/figures/af_test.png", width = 1200, height =1000)
# Set graphical parameters to match your line plot style
par(mar = c(12, 12, 6, 8),  # Bottom, Left, Top, Right margins
    mgp = c(5, 3.0, 0),    # Axis title, labels, line positions
    cex.lab = 2.5,         # Axis label size
    cex.axis = 2.5,        # Tick label size
    cex.main = 3.5)        # Main title size

# Create matrix (keeping your existing data wrangling)
af_matrix <- full_counts_clean |>
  filter(Bird.Call == "Acadian Flycatcher") |>
  select(julian_day, min_bin, n) |>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()

rownames(af_matrix) <- full_counts_clean |>
  filter(Bird.Call == "Acadian Flycatcher") |>
  select(julian_day) |>
  distinct() |>
  pull(julian_day)

# Create heatmap plot
image(af_matrix, 
      axes = FALSE, 
      col = colorRampPalette(c("white", "darkorange"))(256))

# Custom x-axis (DOY)
axis(1, 
     at = tick_at_x, 
     labels = tick_labels_x, 
     las = 2,          # Perpendicular labels
     cex.axis = 2.5)

# Custom y-axis (Time of Day)
axis(2, 
     at = tick_at_y, 
     labels = tick_labels_y, 
     las = 1,          # Horizontal labels
     cex.axis = 2.5)

# Add titles using mtext() for better control
title(main = "Acadian Flycatcher", line = 1)  # line adjusts vertical position
mtext("DOY", side = 1, line = 10, cex = 3.0,font=2)  # Increased line value pushes label down
mtext("TOD (AM)", side = 2, line = 9, cex = 3.0, font=2)  # Increased line pushes label left

dev.off()
```

## Summer Tanager Matrix

```{r}

png("C:/git/MasonFarmARUs/figures/st_test.png", width = 1200, height =1000)
# Set graphical parameters to match your line plot style
par(mar = c(12, 12, 6, 8),  # Bottom, Left, Top, Right margins
    mgp = c(5, 3.0, 0),    # Axis title, labels, line positions
    cex.lab = 2.5,         # Axis label size
    cex.axis = 2.5,        # Tick label size
    cex.main = 3.5)        # Main title size

st_matrix <- full_counts_clean |>
  filter(Bird.Call == "Summer Tanager") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(st_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Summer Tanager")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


image(st_matrix, axes = FALSE, col = colorRampPalette(c("white", "navy"))(256),)

# Custom x-axis (DOY)
axis(1, 
     at = tick_at_x, 
     labels = tick_labels_x, 
     las = 2,          # Perpendicular labels
     cex.axis = 2.5)

# Custom y-axis (Time of Day)
axis(2, 
     at = tick_at_y, 
     labels = tick_labels_y, 
     las = 1,          # Horizontal labels
     cex.axis = 2.5)

# Add titles using mtext() for better control
title(main = "Summer Tanager", line = 1)  # line adjusts vertical position
mtext("DOY", side = 1, line = 10, cex = 3.0,font=2)  # Increased line value pushes label down
mtext("TOD (AM)", side = 2, line = 9, cex = 3.0, font=2)  # Increased line pushes label left
```

## Yellow-throated Vireo Matrix

```{r}

png("C:/git/MasonFarmARUs/figures/yv_test.png", width = 1200, height =1000)
# Set graphical parameters to match your line plot style
par(mar = c(12, 12, 6, 8),  # Bottom, Left, Top, Right margins
    mgp = c(5, 3.0, 0),    # Axis title, labels, line positions
    cex.lab = 2.5,         # Axis label size
    cex.axis = 2.5,        # Tick label size
    cex.main = 3.5)        # Main title size

yv_matrix <- full_counts_clean |>
  filter(Bird.Call == "Yellow-throated Vireo") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(yv_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Yellow-throated Vireo")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)

image(yv_matrix, axes = FALSE, col = colorRampPalette(c("white", "darkgreen"))(256),)

# Custom x-axis (DOY)
axis(1, 
     at = tick_at_x, 
     labels = tick_labels_x, 
     las = 2,          # Perpendicular labels
     cex.axis = 2.5)

# Custom y-axis (Time of Day)
axis(2, 
     at = tick_at_y, 
     labels = tick_labels_y, 
     las = 1,          # Horizontal labels
     cex.axis = 2.5)

# Add titles using mtext() for better control
title(main = "Yellow-throated Vireo", line = 1)  # line adjusts vertical position
mtext("DOY", side = 1, line = 10, cex = 3.0,font=2)  # Increased line value pushes label down
mtext("TOD (AM)", side = 2, line = 9, cex = 3.0, font=2)  # Increased line pushes label left

dev.off()
```

## Eastern Wood-Pewee Matrix

```{r}

png("C:/git/MasonFarmARUs/figures/ep_test.png", width = 1200, height =1000)
# Set graphical parameters to match your line plot style
par(mar = c(12, 12, 6, 8),  # Bottom, Left, Top, Right margins
    mgp = c(5, 3.0, 0),    # Axis title, labels, line positions
    cex.lab = 2.5,         # Axis label size
    cex.axis = 2.5,        # Tick label size
    cex.main = 3.5)        # Main title size

ep_matrix <- full_counts_clean |>
  filter(Bird.Call == "Eastern Wood-Pewee") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(ep_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Eastern Wood-Pewee")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


image(ep_matrix, axes = FALSE, col = colorRampPalette(c("white", "maroon"))(256),)

# Custom x-axis (DOY)
axis(1, 
     at = tick_at_x, 
     labels = tick_labels_x, 
     las = 2,          # Perpendicular labels
     cex.axis = 2.5)

# Custom y-axis (Time of Day)
axis(2, 
     at = tick_at_y, 
     labels = tick_labels_y, 
     las = 1,          # Horizontal labels
     cex.axis = 2.5)

# Add titles using mtext() for better control
title(main = "Eastern Wood-Pewee", line = 1)  # line adjusts vertical position
mtext("DOY", side = 1, line = 10, cex = 3.0,font=2)  # Increased line value pushes label down
mtext("TOD (AM)", side = 2, line = 9, cex = 3.0, font=2)  # Increased line pushes label left

dev.off()
```

## Tufted Titmouse Matrix

```{r}
png("C:/git/MasonFarmARUs/figures/tt_test.png", width = 1200, height =1000)
# Set graphical parameters to match your line plot style
par(mar = c(12, 12, 6, 8),  # Bottom, Left, Top, Right margins
    mgp = c(5, 3.0, 0),    # Axis title, labels, line positions
    cex.lab = 2.5,         # Axis label size
    cex.axis = 2.5,        # Tick label size
    cex.main = 3.5)        # Main title size

tt_matrix <- full_counts_clean |>
  filter(Bird.Call == "Tufted Titmouse") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(tt_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Tufted Titmouse")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


image(tt_matrix, axes = FALSE, col = colorRampPalette(c("white", "purple"))(256),)

# Custom x-axis (DOY)
axis(1, 
     at = tick_at_x, 
     labels = tick_labels_x, 
     las = 2,          # Perpendicular labels
     cex.axis = 2.5)

# Custom y-axis (Time of Day)
axis(2, 
     at = tick_at_y, 
     labels = tick_labels_y, 
     las = 1,          # Horizontal labels
     cex.axis = 2.5)

# Add titles using mtext() for better control
title(main = "Tufted Titmouse", line = 1)  # line adjusts vertical position
mtext("DOY", side = 1, line = 10, cex = 3.0,font=2)  # Increased line value pushes label down
mtext("TOD (AM)", side = 2, line = 9, cex = 3.0, font=2)  # Increased line pushes label left

dev.off()
```

## Scarlet Tanager Matrix

```{r}

png("C:/git/MasonFarmARUs/figures/sct_test.png", width = 1200, height =1000)
# Set graphical parameters to match your line plot style
par(mar = c(12, 12, 6, 8),  # Bottom, Left, Top, Right margins
    mgp = c(5, 3.0, 0),    # Axis title, labels, line positions
    cex.lab = 2.5,         # Axis label size
    cex.axis = 2.5,        # Tick label size
    cex.main = 3.5)        # Main title size

sct_matrix <- full_counts_clean |>
  filter(Bird.Call == "Scarlet Tanager") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(sct_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Scarlet Tanager")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


image(sct_matrix, axes = FALSE, col = colorRampPalette(c("white", "royalblue"))(256),)

# Custom x-axis (DOY)
axis(1, 
     at = tick_at_x, 
     labels = tick_labels_x, 
     las = 2,          # Perpendicular labels
     cex.axis = 2.5)

# Custom y-axis (Time of Day)
axis(2, 
     at = tick_at_y, 
     labels = tick_labels_y, 
     las = 1,          # Horizontal labels
     cex.axis = 2.5)

# Add titles using mtext() for better control
title(main = "Scarlet Tanager", line = 1)  # line adjusts vertical position
mtext("DOY", side = 1, line = 10, cex = 3.0,font=2)  # Increased line value pushes label down
mtext("TOD (AM)", side = 2, line = 9, cex = 3.0, font=2)  # Increased line pushes label left

dev.off()
```

## Arranging these graphs into a panel figure

```{r}

```

```{r}
png("C:/git/MasonFarmARUs/figures/species_matrices.png", width = 1000, height = 1400)

par(mfrow = c(3, 2), mar = c(5, 4, 4, 4))

# Acadian flycatcher 
af_matrix <- full_counts_clean |>
  filter(Bird.Call == "Acadian Flycatcher") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(af_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Acadian Flycatcher")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)

par(mar = c(5, 5, 2, 8))
image(af_matrix, axes = FALSE, col = colorRampPalette(c("white","darkorange"))(256))

axis(1, at = tick_at_x, labels = tick_labels_x, las = 2)

axis(2, at = tick_at_y, labels = tick_labels_y, las = 2) #modify to put hour labels
# Add title and axis labels
title(main = "Acadian Flycatcher", cex.main = 1.5)  # Main title
mtext("DOY", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("TOD (AM)", side = 2, line = 2.5, cex = 1.2)  # Y-axis label


# Summer Tanager 

st_matrix<- full_counts_clean |>
  filter(Bird.Call == "Summer Tanager") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

st_matrix <- full_counts_clean |>
  filter(Bird.Call == "Summer Tanager") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(st_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Summer Tanager")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


par(mar = c(5, 5, 2, 8))
image(st_matrix, axes = FALSE, col = colorRampPalette(c("white", "navy"))(256),)

axis(1, at = tick_at_x, labels = tick_labels_x, las = 2)

axis(2, at = tick_at_y, labels = tick_labels_y, las = 2) #modify to put hour labels
# Add title and axis labels
title(main = "Summer Tanager", cex.main = 1.5)  # Main title
mtext("DOY", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("TOD (AM)", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Yellow-throated Vireo 
yv_matrix <- full_counts_clean |>
  filter(Bird.Call == "Yellow-throated Vireo") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(yv_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Yellow-throated Vireo")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


par(mar = c(5, 5, 2, 8))
image(yv_matrix, axes = FALSE, col = colorRampPalette(c("white", "darkgreen"))(256),)

axis(1, at = tick_at_x, labels = tick_labels_x, las = 2)

axis(2, at = tick_at_y, labels = tick_labels_y, las = 2) #modify to put hour labels
# Add title and axis labels
title(main = "Yellow-throated Vireo", cex.main = 1.5)  # Main title
mtext("DOY", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("TOD (AM)", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Eastern Wood-Pewee
ep_matrix <- full_counts_clean |>
  filter(Bird.Call == "Eastern Wood-Pewee") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(ep_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Eastern Wood-Pewee")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


par(mar = c(5, 5, 2, 8))
image(ep_matrix, axes = FALSE, col = colorRampPalette(c("white", "maroon"))(256),)

axis(1, at = tick_at_x, labels = tick_labels_x, las = 2)

axis(2, at = tick_at_y, labels = tick_labels_y, las = 2) #modify to put hour labels
# Add title and axis labels
title(main = "Eastern Wood-Pewee", cex.main = 1.5)  # Main title
mtext("DOY", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("TOD (AM)", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Tufted Titmouse 
tt_matrix <- full_counts_clean |>
  filter(Bird.Call == "Tufted Titmouse") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(tt_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Tufted Titmouse")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


par(mar = c(5, 5, 2, 8))
image(tt_matrix, axes = FALSE, col = colorRampPalette(c("white", "purple"))(256),)

axis(1, at = tick_at_x, labels = tick_labels_x, las = 2)

axis(2, at = tick_at_y, labels = tick_labels_y, las = 2) #modify to put hour labels
# Add title and axis labels
title(main = "Tufted Titmouse", cex.main = 1.5)  # Main title
mtext("DOY", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("TOD (AM)", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Scarlet Tanager 
sct_matrix <- full_counts_clean |>
  filter(Bird.Call == "Scarlet Tanager") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()
rownames(sct_matrix) <- full_counts_clean|>
  filter(Bird.Call == "Scarlet Tanager")|>
  select(julian_day)|>
  distinct()|>
  pull(julian_day)


par(mar = c(5, 5, 2, 8))
image(sct_matrix, axes = FALSE, col = colorRampPalette(c("white", "royalblue"))(256),)

axis(1, at = tick_at_x, labels = tick_labels_x, las = 2)

axis(2, at = tick_at_y, labels = tick_labels_y, las = 2) #modify to put hour labels
# Add title and axis labels
title(main = "Scarlet Tanager", cex.main = 1.5)  # Main title
mtext("DOY", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("TOD (AM)", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

dev.off()
```
