---
title: "K9_Analysis"
author: "Grace Layman"
date: "2025-04-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis on K9 Stake 2022

## Total amount of species observed

```{r}
#Loading necessary libraries 
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(tibble)
```

```{r}
# Looking at Species Observations Across the Year 
k9_total <- read.csv("C:/git/MasonFarmARUs/data/2022_k9_filtered.csv")
speciesList <- read.csv("C:/git/MasonFarmARUs/data/species_list_csvCopy.csv")
species <- speciesList$Common.Name
julian_days <- 151:201
complete_days <- crossing(Common.name = species, julian_day = julian_days)

num_species <- k9_total |>
  count(Common.name)|>
  arrange(desc(n))|>
  glimpse()


# Want to make a dataframe that has all the combinations of julian days and species
species_by_day <- k9_total |>
  group_by(julian_day,)|>
  count(Common.name)|>
  arrange(desc(n)) |>
  glimpse()

species_day <- complete_days|>
  left_join(species_by_day, by = c("Common.name", "julian_day"))|>
  mutate(n = replace_na(n,0))

#write.csv(species_day,"data/species_by_day.csv")
```

I will be looking at seasonal and temporal variation in species abundance with the six species that were observed the most by Birdnet over the summer. This data is stored in the num_species data frame above. In order, these species are: Acadian Flycatcher, Summer Tanager, Yellow-throated Vireo, Eastern Wood-Pewee, Tufted Titmouse, and Scarlet Tanager.

## Basic Stats on Observations

```{r}
k9_stats<- k9_total%>%
  group_by(Common.name) %>% 
  summarize(medianConf = median(Confidence),
            maxConf = max(Confidence),
            minConf = min(Confidence)) %>% 
  arrange(desc(maxConf)) %>% data.frame()|>
  glimpse()
```

## Trends Across the Six Species

```{r plotting-jdVspecies, fig.path='figures/k9/'}

#png("C:/git/MasonFarmARUs/figures/jdVdect.png", width = 800, height = 600)

#Mapping Julian Day Versus the Number of Observations for the top Seven Species
filtered_AF <- species_day[species_day$Common.name == "Acadian Flycatcher", ]
plot(filtered_AF$julian_day,
     filtered_AF$n, 
     xlab = "Julian Day",
     ylab = "Number of Vocalizations", 
     ylim = c(0, 1000), xlim = c(151,201),
     type = 'l',
     col = 'lightgoldenrod', 
     lwd = 2)
filtered_ST <- species_day[species_day$Common.name == "Summer Tanager", ]
points(filtered_ST$julian_day, 
       filtered_ST$n,
       type = 'l',
       col = "lightblue",
       lwd = 2)
filtered_YV <- species_day[species_day$Common.name == "Yellow-throated Vireo", ]
points(filtered_YV$julian_day, 
       filtered_YV$n,
       type = 'l',
       col = "lightgreen",
       lwd = 2)
filtered_EP <- species_day[species_day$Common.name == "Eastern Wood-Pewee", ]
points(filtered_EP$julian_day, 
       filtered_EP$n,
       type = 'l',
       col = "lightcoral",
       lwd = 2)
filtered_TT <- species_day[species_day$Common.name == "Tufted Titmouse", ]
points(filtered_TT$julian_day, 
       filtered_TT$n,
       type = 'l',
       col = "plum3",
       lwd = 2)
filtered_SCT <- species_day[species_day$Common.name == "Scarlet Tanager", ]
points(filtered_SCT$julian_day, 
       filtered_SCT$n,
       type = 'l',
       col = "royalblue",
       lwd = 2)
legend("topright", legend = c("Acadian Flycatcher",
                              "Summer Tanager",
                              "Yellow-throated Vireo",
                              "Eastern Wood-Pewee",
                              "Tufted Titmouse",
                              "Scarlet Tanager"),
       col = c("lightgoldenrod", "lightblue", "lightgreen", "lightcoral", "plum3", "royalblue"),
       lwd = 2)
#dev.off()
```

```{r}
# Full dataframe with minute bins 

day_mins<- k9_total |>
  rename("start" = "Start..s.", "end" = "End..s.")|> # Comment this out if you have already run this line
  mutate(min_bin = ceiling(end/900))

# Creating a dataframe with every species, min_bin, and date possible 

all_julian <- min(k9_total$julian_day):max(k9_total$julian_day)
species_vec <- speciesList$Common.Name
julian_vec <- as.integer(all_julian)
min_bin_vec <- day_mins$min_bin

all_combos <- expand.grid(
  Bird.Call = species_vec,
  julian_day = julian_vec,
  min_bin = min_bin_vec
)

target_species <- c(
  "Acadian Flycatcher", 
  "Summer Tanager", 
  "Yellow-throated Vireo", 
  "Eastern Wood-Pewee", 
  "Tufted Titmouse", 
  "Scarlet Tanager"
)
```

## Matrix Mapping

```{r}

bird_counts <- day_mins |>
  filter(Common.name %in% target_species)|>
  count(Common.name, julian_day, min_bin)

full_counts <- all_combos |>
  filter(Bird.Call %in% target_species)|>
  left_join(bird_counts, by = c("Bird.Call" = "Common.name", "julian_day", "min_bin")) |>
  mutate(n = replace_na(n, 0))

# Get unique combinations of Bird.Call, julian_day, min_bin, and n
full_counts_clean <- full_counts |>
  distinct(Bird.Call, julian_day, min_bin, n, .keep_all = TRUE)
write.csv(full_counts_clean,"C:/git/MasonFarmARUs/data/full_counts_clean.csv")
```

### Acadian Flycatcher Matrix

```{r}
af_matrix <- full_counts_clean |>
  filter(Bird.Call == "Acadian Flycatcher") |>
  select(julian_day, min_bin, n)|>
  pivot_wider(
    names_from = min_bin,
    values_from = n
  ) |>
  select(-julian_day) |>
  as.matrix()

image(af_matrix, axes = FALSE, col = colorRampPalette(c("white","yellow", "lightgoldenrod","lightgoldenrod3", "yellow4"))(256))

axis(1, at = seq(0, 1, length.out = ncol(af_matrix)), labels = colnames(af_matrix), las = 2)

# axis(2, at = seq(0, 1, length.out = nrow(af_matrix)), labels = rownames(af_matrix)) #modify to put hour labels
# Add title and axis labels
title(main = "Acadian Flycatcher Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
#mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Summer Tanager Matrix

```{r}
st_matrix<- full_counts_clean |>
  filter(Bird.Call == "Summer Tanager") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

st_matrix_numeric <- st_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(st_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "lightblue", "skyblue2","skyblue3", "navy"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(st_matrix_numeric)), labels = colnames(st_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(st_matrix_numeric)), labels = rownames(st_matrix_numeric))
# Add title and axis labels
title(main = "Summer Tanager Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Yellow-throated Vireo Matrix

```{r}
yv_matrix<- full_counts_clean |>
  filter(Bird.Call == "Yellow-throated Vireo") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

yv_matrix_numeric <- yv_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(yv_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white","lightgreen", "mediumspringgreen", "green", "darkgreen"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(yv_matrix_numeric)), labels = colnames(yv_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(yv_matrix_numeric)), labels = rownames(yv_matrix_numeric))
# Add title and axis labels
title(main = "Yellow-throated Vireo Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Eastern Wood-Pewee Matrix

```{r}
ep_matrix<- full_counts_clean |>
  filter(Bird.Call == "Eastern Wood-Pewee") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

ep_matrix_numeric <- ep_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(ep_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white","pink", "maroon1","maroon3","maroon4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(ep_matrix_numeric)), labels = colnames(ep_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(ep_matrix_numeric)), labels = rownames(ep_matrix_numeric))
# Add title and axis labels
title(main = "Eastern Wood-Pewee Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Tufted Titmouse Matrix

```{r}
tt_matrix<- full_counts_clean |>
  filter(Bird.Call == "Tufted Titmouse") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

tt_matrix_numeric <- tt_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(tt_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "plum2","plum", "purple","purple4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(tt_matrix_numeric)), labels = colnames(tt_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(tt_matrix_numeric)), labels = rownames(tt_matrix_numeric))
# Add title and axis labels
title(main = "Tufted Titmouse Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Scarlet Tanager Matrix

```{r}
sct_matrix<- full_counts_clean |>
  filter(Bird.Call == "Scarlet Tanager") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

sct_matrix_numeric <- sct_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(sct_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "turquoise1", "turquoise","turquoise3", "turquoise4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(tt_matrix_numeric)), labels = colnames(sct_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(sct_matrix_numeric)), labels = rownames(sct_matrix_numeric))
# Add title and axis labels
title(main = "Scarlet Tanager Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label
```

## Arranging these graphs into a panel figure

```{r}
png("C:/git/MasonFarmARUs/figures/species_heatmaps.png", width = 800, height = 1200)

par(mfrow = c(3, 2), mar = c(5, 4, 4, 4))

# Acadian flycatcher 
af_matrix <- full_counts_clean |>
  filter(Bird.Call == "Acadian Flycatcher") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

af_matrix <- af_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(af_matrix, axes = FALSE, col = colorRampPalette(c("white","yellow", "lightgoldenrod","lightgoldenrod3", "yellow4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(af_matrix)), labels = colnames(af_matrix), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(af_matrix)), labels = rownames(af_matrix))
# Add title and axis labels
title(main = "Acadian Flycatcher Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Summer Tanager 

st_matrix<- full_counts_clean |>
  filter(Bird.Call == "Summer Tanager") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

st_matrix_numeric <- st_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(st_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "lightblue", "skyblue2","skyblue3", "navy"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(st_matrix_numeric)), labels = colnames(st_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(st_matrix_numeric)), labels = rownames(st_matrix_numeric))
# Add title and axis labels
title(main = "Summer Tanager Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Yellow-throated Vireo 
yv_matrix<- full_counts_clean |>
  filter(Bird.Call == "Yellow-throated Vireo") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

yv_matrix_numeric <- yv_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(yv_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white","lightgreen", "mediumspringgreen", "green", "darkgreen"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(yv_matrix_numeric)), labels = colnames(yv_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(yv_matrix_numeric)), labels = rownames(yv_matrix_numeric))
# Add title and axis labels
title(main = "Yellow-throated Vireo Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Eastern Wood-Pewee
ep_matrix<- full_counts_clean |>
  filter(Bird.Call == "Eastern Wood-Pewee") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

ep_matrix_numeric <- ep_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(ep_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white","pink", "maroon1","maroon3","maroon4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(ep_matrix_numeric)), labels = colnames(ep_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(ep_matrix_numeric)), labels = rownames(ep_matrix_numeric))
# Add title and axis labels
title(main = "Eastern Wood-Pewee Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Tufted Titmouse 
tt_matrix<- full_counts_clean |>
  filter(Bird.Call == "Tufted Titmouse") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

tt_matrix_numeric <- tt_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(tt_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "plum2","plum", "purple","purple4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(tt_matrix_numeric)), labels = colnames(tt_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(tt_matrix_numeric)), labels = rownames(tt_matrix_numeric))
# Add title and axis labels
title(main = "Tufted Titmouse Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

# Scarlet Tanager 
sct_matrix<- full_counts_clean |>
  filter(Bird.Call == "Scarlet Tanager") |>
  select(-Bird.Call)|>
  pivot_wider(
    names_from = julian_day,
    values_from = n
  ) 

sct_matrix_numeric <- sct_matrix |>
  column_to_rownames(var = "min_bin")|>
  as.matrix()

image(sct_matrix_numeric, axes = FALSE, col = colorRampPalette(c("white", "turquoise1", "turquoise","turquoise3", "turquoise4"))(256),)

axis(1, at = seq(0, 1, length.out = ncol(tt_matrix_numeric)), labels = colnames(sct_matrix_numeric), las = 2)
axis(2, at = seq(0, 1, length.out = nrow(sct_matrix_numeric)), labels = rownames(sct_matrix_numeric))
# Add title and axis labels
title(main = "Scarlet Tanager Observations", cex.main = 1.5)  # Main title
mtext("Julian Day", side = 1, line = 2.5, cex = 1.2)  # X-axis label
mtext("15 minute intervals", side = 2, line = 2.5, cex = 1.2)  # Y-axis label

dev.off()
```
